---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# JTT (v0.1.0)

<!-- badges: start -->
<!-- badges: end -->

This package implements consistent clustering for group-wise linear regression with graph structure.

**cite this package:**   
Ohishi, M. (2025). JTT: Consistent clustering for group-wise linear regression. R package version 0.1.0. https://github.com/ohishim/JTT 

## Installation

You can install the R package `JTT` like so:

```{r eval=F}
# install.packages("devtools")
devtools::install_github("ohishim/JTT")
library(JTT)
```

## Example

You can get simulation data by `genData()` and implement JTT method by `JTT()`.
The simulation data is generated as

```{r}
n0 <- 50; p <- 20
Data <- genData(n0, p, SNR=3)
```

You can obtain true clusters as

```{r}
Data$cluster
```

Then, JTT method is implemented as

```{r}
y <- Data$y; X <- Data$X; group <- Data$group; adj <- Data$adj
res <- JTT(y, X, group, adj)
```

Estimated clusters are

```{r}
res$cluster
```

